Efficient pedigree recording for fast population genetics simulation

### 2017-12-28 forwards_paper.tex
fix typo
add comment
add comment that algos look good

Here we describe the simplification algorithm.
The flow is close to our implementation,
but the description below uses set operations,
while in the implementation,
all ancestors are maintained as linked lists of segments
ordered by left endpoint.
As it goes, the algorithm
records a list $M$ that gives the mapping
from input nodes to output nodes,
so that if $M[p] = u$ then the $p^\text{th}$ node in the input
is the same as the $u^\text{th}$ node in the output.
The current state of the algorithm is recorded in $\Al$,
a list of ancestors
each of which is a collections of ancestral segments.
An ancestral segment is a triple $(\ell, r, x)$,
indicating that the output node $x$ inherits from this ancestor
on the genomic segment $[\ell, r)$.

@@

\algstep{S0.}{Initialize.}{
    Set $\Al[j] \leftarrow (0, L, j)$
    and $\Nt_O[j] \leftarrow \Nt_I[S[j]]$ for $0 \le j < \len(S)$.
    Set the current input parent index to $p=0$
    and $M[u] \leftarrow -1$ for $0 \le u < \len(\Nt_I)$.
}

\algstep{S1.}{Input parent loop.}{Set $Q \leftarrow \emptyset$.
}

@@

@@

\begin{figure}
    \includegraphics[]{sims/memuse_nosel}
    \caption{\label{sfig:ramnosel}Peak RAM use in gigabytes (GB) for simulations without selection.  The plots are from
    the same data as in Figure \ref{sfig:rawspeed_nosel}.}
\end{figure}

\end{document}

>>>>

Here we describe the simplification algorithm.
The flow is close to our implementation,
but the description below uses set operations,
while in the implementation,
all ancestors are maintained as linked lists of segments
ordered by left endpoint.
As it goes, the algorithm
records a list $M$ that gives the mapping
from input nodes to output nodes,
so that if $M[p] = u$ then the $p^\text{th}$ node in the input
is the same as the $u^\text{th}$ node in the output.
The current state of the algorithm is recorded in $\Al$,
a list of ancestors
each of which is a collection of ancestral segments.
An ancestral segment is a triple $(\ell, r, x)$,
indicating that the output node $x$ inherits from this ancestor
on the genomic segment $[\ell, r)$.

@@

\algstep{S0.}{Initialize.}{
    Set $\Al[j] \leftarrow (0, L, j)$
    and $\Nt_O[j] \leftarrow \Nt_I[S[j]]$ for $0 \le j < \len(S)$.
    Set the current input parent index to $p=0$
    and $M[u] \leftarrow -1$ for $0 \le u < \len(\Nt_I)$.
}
\krt{We need a verbal definition of $Q$}
\algstep{S1.}{Input parent loop.}{Set $Q \leftarrow \emptyset$.
}

@@

\end{taocpalg}
\krt{I think the algo discussion is  clear.  I've not tried to implement it, which would be the real test, but I find the description fine other than needing to define $Q$ when first used.}

@@

\begin{figure}
    \includegraphics[]{sims/memuse_nosel}
    \caption{\label{sfig:ramnosel}Peak RAM use in gigabytes (GB) for simulations without selection.  The plots are from
    the same data as in Figure \ref{sfig:rawspeed_nosel}.}
\end{figure}
\end{document}
